Loop

### 2019-01-18 Loop.Rmd
some old changes

```{r}
library(readr)
library(dplyr)
library(metafor)
library(devtools)
library(patchwork)
```

@@

```{r}
source("D:/Susi/garvan/Github/mice_sex_diff/mice_sex_diff_Nov/R/meta_analysis.R")
source("D:/Susi/garvan/Github/mice_sex_diff/mice_sex_diff_Nov/R/data_load_clean2.R")
source("D:/Susi/garvan/Github/mice_sex_diff/mice_sex_diff_Nov/R/calc_pop_stats.R")
```

>>>>

```{r}
# library(readr)
# library(dplyr)
# library(metafor)
# library(devtools)
# library(patchwork)

# loading packages - need pacman loaded
pacman::p_load(readr, dplyr, metafor, devtools)
devtools::install_github("thomasp85/patchwork")

@@

```{r}
source("./R/meta_analysis.R")
source("./R/data_load_clean.R") # we need to replcae it with data_load_clean2.R
source("./R/calc_pop_stats.R")
```
